\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-02-05 ZpL/ZpL.tex
Trivial change
Addressing Tristan's comment on y'^2 and adding comment on diffused digits in matrices

When computing with real and $p$-adic fields, exact results are usually impossible,
since most elements have infinite decimal or $p$-adic expansions.
Working with these fields thus requires an analysis of how precision evolves
through the sequence of steps involved in carrying out a computation.
In this paper, we describe a package for computing with $p$-adic rings and fields,
based on a series of papers by the same authors
\cite{caruso-roe-vaccon:14a,caruso-roe-vaccon:15,caruso-roe-vaccon:16,caruso-roe-vaccon:17}.
The core of the package is a method for tracking precision using $p$-adic lattices which
can yield dramatically more precise results, at the cost of increased runtime and memory usage.

@@

In \cite{LV16}, the behavior of the precision when solving
$p$-adic differential equations with separation of 
variables has been studied.
The authors have investigated the gap that appears
when applying a Newton-method solver between
the theoretic loss in precision and the 
actual loss in precision for a naive implementation in \verb?Zp(p)?.
We can reach this theoretical loss in precision using \ZpL.
We use a generic {\color{function}\verb?Newton_Iteration_Solver?}\verb?(g,h,N)?
that applies \verb?N? steps of the Newton method for 
$y'=g \times h(y)$ as described in \cite{LV16}.

@@

>>>>

When computing with real and $p$-adic fields, exact results are usually impossible,
since most elements have infinite decimal or $p$-adic expansions.
Working with these fields thus requires an analysis of how precision evolves
through the sequence of steps involved in carrying out a computation.
In this paper, we describe a package for computing with $p$-adic rings and fields \cite{trac:23505},
based on a series of papers by the same authors
\cite{caruso-roe-vaccon:14a,caruso-roe-vaccon:15,caruso-roe-vaccon:16,caruso-roe-vaccon:17}.
The core of the package is a method for tracking precision using $p$-adic lattices which
can yield dramatically more precise results, at the cost of increased runtime and memory usage.

@@

In \cite{LV16}, the authors studied the computation of isogenies between elliptic curves
over finite fields by applying the lattice precision model to $p$-adic
differential equations.  Specifically, they considered the equation
$y'=g(x) \times h(y)$ with
$g,h,y \in \mathbb{Z}_p \llbracket x \rrbracket$
such that $g(0)=h(0)=1$ and $y(0)=0.$

Their main result was that the intrinsic loss in precision
when computing the coefficient $x^n$ of $y$
from $g$ and $h$ was in $\log_p(n)$
even though a naive analysis of
the Newton method for solving the equation
yield a loss in $\log_p(n)^2.$

We can reach this theoretical loss in precision using \ZpL, while \ZpCR does not perform as well.
We apply \verb?N? steps of the Newton method for 
$y'=g \times h(y)$ as described in \cite{LV16}, using a generic {\color{function}\verb?Newton_Iteration_Solver?}\verb?(g,h,N)?.

@@

Diffused digits frequently arise in practice.  In the context of the matrix multiplication
example of \S \ref{ssec:linalg}, we get

{\noindent \small
\begin{tabular}{rl}
\cIn & \verb?L.?{\color{method}\verb?number_of_diffused_digits?}\verb?(M.?{\color{method}\verb?list?}\verb?())? \\
\cZpLC & \verb?11? \\
\end{tabular}}
